Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-18 WRITEUP/ms.tex

The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower). In \Sec{eqn}, we describe the method used to identify molecular gas complexes and present the formalism within which we interpret the results. In \Sec{results}, we present the results and the scaling relations for the MCs. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
%

@@

The simulation zooms on a galaxy named \flower whose properties are given in \citet{Pallottini17b} and are briefly summarized in the following. \flower is a Lyman-break galaxy (LBG), that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc; \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne. Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    Star formation history of \flower (top) and projected stellar mass distribution (bottom) during {\it (a)} an accretion phases at its early stage of evolution; {\it (b)} a major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.
\label{fig:SFH}}
\end{figure*}

@@

The \SF history of \flower is shown in \Fig{SFH}. The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{Note that here the SFR is calculated based on the stallar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass. The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contributions from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the few hundred Myr simulated in the simulation.

Given the stochasticity in the \SF history of \flower, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}). The two phases correspond to (a) when \flower is accreting materials from its surrounding  and (b) when \flower is undergoing a starburst phase; such phases are expected to bracket the most extreme variations in the cloud dynamics. For completeness, for the other evolutionary stages traced in the simulation we only show the results in terms of the found scaling relations (see \Fig{alpha16-28}).

\AP{i think we need a different name for these objects}
Throughout this paper, we call ``satellite galaxies'' as dense gas regions outside the main disk of \flower, which is $\sim$\,1\,kpc in radius.

@@

\subsection{Structure Identification}\label{sec:method}

To identify the molecular complexes, we use a customized version of the ``clump-finding'' algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones of the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. In the customized version used for this study, we modify the function to enhance the stability of the code.
%
Due to the nature of our AMR simulation, we regrid the simulation data into uniform grids. The grid size is defined based on the highest resolution of the simulation data, i.e., the less refined regions are supersampled in the resulting uniform grids.

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{H$_2$ number density distribution of \flower taken from the accretion phase shown in \Fig{SFH}.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples of MCs identified by the clump-finder. \flower is shown in its in the accreting phase: white contours indicate the identified clumps and the color-bar shows the mean H$_2$ number density, weighted by gas mass. Different rows shows the clump-finder results obtained by applying different H$_2$ number density. Left and right panels show the galaxy from different inclinations
%cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see \Sec{method})
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show the H$_2$ number density ($n_{\rm H2}$) distribution of \flower~in its accreting phase, by inlcuding the contribution from the gas within 3.5 kpc from the galaxy center.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$ density field is significantly larger then zero. Such functional is a measure of the Euler characteristic, being positive (negative) implies that the field is made of isolated (connected) components. See Fig. 6 in \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work (see \Sec{ncut}).} to each snapshot.

To have a visual overwview of the clump finding results, in \Fig{MC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps.
% equation below for bookkeeping:
% ${\rm pixel_i}$\eq$\frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}$,
% where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt
% to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MC}) --- so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such as the H$_2$ gas mass ($M_{\rm cl}$), effective size ($R$), Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.

The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate
each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is
calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MC.
The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.\label{ftn:veldisp}}.
On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MC distributions in terms of their molecular gas masses, radii, and gas mass fractions, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass within the MC volume.
%
We note that the distributions vary for different evolutionary stage of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of the order of 10$^{5.5}$\,\Msun for the densest MC.
%
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work,
for each of the given $n_{\rm cut}$ (see \Sec{method}). The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.

@@

%\section{Basic physical properties}\label{sec:eqn}

%\subsection{Virial Equilibrium and Larson's Relations}\label{sec:PVE}
\subsection{Larson's Relations}\label{sec:PVE}

In next sections, we examine and compare properties of the MCs with observations in the context of the Larson's relations \citep{Larson81a}. Namely, the linewidth-size, density-size, and mass-size relations. Larson's relations are adopted for the discussion in this work as they  describe the interactions between gravity and turbulence, and is the first set of relations used for studying star-forming molecular structure formation based on observables which has been routinely used for comparing properties of molecular structures in different galactic environments.
% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
In general, the virial theorem for a distribution of gas can be written as
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot{\mathcal{I}} = 2(\mathcal{T} - \mathcal{T}_{\rm ext}) + \mathcal{W},
\end{equation}
where $\ddot{\mathcal{I}}$ is the second time derivative of the Lagrangian moment of inertia, 
$\mathcal{T}$ is the internal energy of the gas, 
$\mathcal{T}_{\rm ext}$ is external pressure support, and $\mathcal{W}$ is the gravitational energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and velocity dispersion $\sigma$, accounting for both thermal and turbulent velocity dispersion. Neglecting magnetic field and calling $P_{\rm ext}$ the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}{\mathcal{I}} = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R - \frac{\Gamma GM_{\rm cl}^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the first term on the right hand side (RHS) is the pressure term from internal velocity dispersion, the second term the external pressure term, and the third term is is the gravity term. For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure), \Eq{virial} becomes:
\begin{equation}
\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma GM_{\rm cl}/R} = \frac{5\sigma^2R}{GM_{\rm cl}}\,,
\label{eqn:alpha}
\end{equation}
which is also the defined as the virial parameter $\alpha_{\rm vir}$.

Motivated by the Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a},
we recast Equation~\ref{eqn:alpha} into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5\,,
\label{eqn:SVE}
\end{equation}
for gas in virial equilibrium (i.e., by setting $\alpha_{\rm vir}$\eq1).
On the other hand, for pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes:
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M_{\rm cl}}{4\pi R^3} - \frac{\Gamma G M_{\rm cl}^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes how much external pressure is needed to confine the gas inside a given volume.
Substituting surface density $\Sigma$\eq$M/\pi R^2$ into Equation~\ref{eqn:pext}, we can express it with the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right)\,,
\label{eqn:v0}
\end{equation}
keeping $\sigma^2/R$ on the LHS.

Based on Equations~\ref{eqn:SVE} and \ref{eqn:pext}, a one-to-one mapping
between $\sigma^2/R$ and $\Sigma$ is therefore expected for a virialized cloud,
since $\sigma^2/R\propto\Sigma$. Equation~\ref{eqn:v0}
then yields the loci along which external pressures $P_{\rm ext}$ are needed in order for some given MCs to have
linewidths $\sigma$ for a given set of surface densities. % (see\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with
external pressure $P_{\rm ext}$ (and therefore $\sigma^2/R$ is not constant
with $\Sigma$ but varies depending on $P_{\rm ext}$; cf.
expectation for SVE, where $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

>>>>

The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}. We start by providing some physical background in \Sec{Back}. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower). In \Sec{eqn}, we describe the method used to identify molecular gas complexes and present the formalism within which we interpret the results. In \Sec{results}, we present the results and the scaling relations for the MCs. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
%
\section{Physical Background}\label{sec:Back}
We begin by introducing some basic material concerning known physical relations and stability analysis of MCs that will become useful in the following.
\subsection{Larson relations}\label{sec:PVE}
\citep{Larson81a} discussed a number of relations among Galactic MC properties, namely the linewidth-size, density-size, and mass-size relations. Larson relations are routinely used for comparing properties of molecular structures in different galactic environments. They also represent a useful framework to analyze our results as they arise from the interplay between gravity and turbulence encoded in the virial theorem.

In general, the virial theorem for a gas distribution of gas can be written as
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot{\mathcal{I}} = 2(\mathcal{T} - \mathcal{T}_{\rm ext}) + \mathcal{W},
\end{equation}
where $\ddot{\mathcal{I}}$ is the second time derivative of the Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and $\mathcal{W}$ is the gravitational energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and r.m.s. velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions. Neglecting magnetic field and defining $P_{\rm ext}$ the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM_{\rm cl}^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the r.h.s. represent the kinetic, external, and gravity pressure terms. 
%
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure), \Eq{virial} becomes:
\begin{equation}
\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma (GM_{\rm cl}/R)} = \frac{5\sigma^2R}{GM_{\rm cl}}\,,
\label{eqn:alpha}
\end{equation}
which defined as the virial parameter $\alpha_{\rm vir}$.

Motivated by the Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we recast Equation~\ref{eqn:alpha} into 
\begin{equation}
\sigma^2/R = \pi G \Sigma/5\,,
\label{eqn:SVE}
\end{equation}
for gas in virial equilibrium, i.e., by setting $\alpha_{\rm vir}$\eq1; the surface density $\Sigma$\eq$M/\pi R^2$. On the other hand, for pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with external pressure), Equation~\ref{eqn:virial} becomes:
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M_{\rm cl}}{4\pi R^3} - \Gamma\frac{G M_{\rm cl}^2}{4\pi R^4}\,,
\label{eqn:pext}
\end{equation}
which quantifies the external pressure needed to confine the gas inside a given volume. Substituting again $\Sigma$  into Equation~\ref{eqn:pext}, we find 
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right)\,,
\label{eqn:v0}
\end{equation}
keeping $\sigma^2/R$ on the LHS.

Based on Equations~\ref{eqn:SVE} and \ref{eqn:pext}, a one-to-one mapping between $\sigma^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma^2/R\propto\Sigma$. Equation~\ref{eqn:v0} then yields the loci along which external pressures $P_{\rm ext}$ are needed in order for some given MCs to have linewidths $\sigma$ for a given set of surface densities. In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with external pressure $P_{\rm ext}$; therefore $\sigma^2/R$ is not constant with $\Sigma$ but varies depending on $P_{\rm ext}$ (cf. expectation for SVE, where $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

Summarizing, the virial parameter can be used to quantify the stability/boundedness of an MC. Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
%
Such criterion is often used in \obs \citep[see e.g., ][]{Kauffmann17b}; in the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.

%\subsection{Gravitational Instabilities}\label{sec:Q}
\subsection{Toomre stability analysis}\label{sec:Q}

In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy  $v_{\rm circ}/\sigma$, i.e., the circular velocity to dispersion ratio \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis
For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of finite thickness $h$ is described by
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2\,,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,.
\label{eqn:kappa}
\end{equation}
\citep{Romeo92a}.
The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support. The Toomre $Q$ parameter for the gas component can be defined as \citep{Toomre64a}:
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma_{\rm gas}\kappa}{\pi G \Sigma_{\rm gas}}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). Physically, this situation occurs when local gravitational instability
overcomes support from pressure and rotation, allowing fragmentation and collapse to happen. Similarly, for a collisionless fluid --- as an ensemble of stars --- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
\begin{equation}
Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
\end{equation}

In our stability analysis, we account for the non-negligible disk thickness and for the combined effect of gas and stars; this is done adopting the approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
%
The effect of disk thickness modify the $Q$ parameter for gas/star by accounting for the vertical velocity dispersion:
\begin{equation}
T_{x} = \left\{
		\begin{array}{lccr}
			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r
\\
		\end{array}
	\right.
\end{equation}
and
\begin{equation}
Q^{\rm thick}_{x} = T_{x} Q\,,
\end{equation}
with $x$ indicating either gas or stars.
% Note that w/ thickness, there's the a self-gravity dilution term in the dispersion relation, which in effect reduceds the surface gravity in the vertical direction. As such, it is easier to be stable against gravitaional instability. Thus, the criterion for instability $Q$ is reduced.
%
The combined effect of gas and stars can then be accounted for by writing
\begin{equation}\label{eqn:q_eff}
Q^{-1}_{\rm eff} =  \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{Q^{\rm thick}_{\star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\star} \leq Q^{\rm thick}_{\rm gas} \\
				\end{array}
			    \right.
\end{equation}
where the relative weight $w$ is defined as:
\begin{equation}
w\equiv\frac{2 \sigma_{\star} \sigma_{\rm gas}}{\sigma_{\star}^2 + \sigma_{\rm gas}^2},
\end{equation}
Conceptually, the thickness of a disk reduces the gravity in the vertical direction, thereby making it easier for a system to obtain stability, and thus lowering the criterion of the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to 
0.67 \citep{Goldreich65a}.
%
On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus, increasing the criterion of the Toomre $Q_{\rm crit}$, unless it is dynamically hot to ``compensate''. As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2

@@

The simulation zooms on a galaxy named \flower whose properties are given in \citet{Pallottini17b} and are briefly summarized in the following. \flower is a Lyman-break galaxy (LBG), that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc; \flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne. Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top panel}: Star formation history of \flower. {\it Bottom}: projected stellar mass distribution during {\it (a)} an early accretion phase;  {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
\label{fig:SFH}}
\end{figure*}

@@

The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass. The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}. The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.

Given \flower's SF stochastic nature, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}). The two phases correspond to (a) intense accretion (b) starburst (\Fig{SFH}). We are interesting in determining whether MC properties are sensitive to these different dynamical conditions. For completeness, for the other evolutionary stages traced in the simulation we only show scaling relations (see \Fig{alpha16-28}).

Throughout this paper, we dub as ``satellite galaxies'' the dense gas regions outside the main disk of \flower. The distinction between clumps and satellites is admittedly somewhat ambiguous, and we consider it only as a working one.
\AF{To be discussed at the end}

@@

\subsection{Identification}\label{sec:method}

To identify the molecular complexes, we use a customized version of the ``clump-finding'' algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones of the simulation into non-overlapping tiles, which are stored in a $k$-dimensional tree ($k$-D tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. In the customized version used for this study, we modify the function to enhance the stability of the code.
%
Due to the nature of our AMR simulation, we regrid the simulation data into uniform grids. The grid size is defined based on the highest resolution of the simulation data, i.e., the less refined regions are supersampled in the resulting uniform grids.

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{Probability distribution function of the H$_2$ number density in \flower during the accretion phase shown in \Fig{SFH}.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples of MCs (white contours) identified by the clump-finder in  \flower during its  accreting phase. The color-bar shows the mean H$_2$ number density, weighted by gas mass. Different rows shows the clump-finder results obtained by applying different H$_2$ number density cuts density cuts $(n_{\rm cut})$ as shown by the label. Left and right panels show the galaxy from different viewing angles.
\label{fig:MC}}
\end{figure*}

In \Fig{h2density}, we show the H$_2$ number density ($n_{\rm H2}$) distribution of \flower~in its accreting phase, by including the contribution from the gas within 3.5 kpc from the galaxy center.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$ density field is significantly larger than zero. This implies that the field is made of isolated components. See Fig. 6 in \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm cut}/{\rm cm^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 5.81, 11.36, 18.96, 31.62]$\footnote{We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).} to each snapshot.

To visually appreciate  the clump finding procedure, in \Fig{MC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MC}) so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such as the gas mass ($M_{\rm cl}$), effective size ($R$), Mach number ($\mathcal{M}$), r.m.s. velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.

The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MC.
%
The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}. On average, the Mach number of the MCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MC mass of the order of 10$^{5.5}$\,\Msun for the densest MC.
%
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do you show the valu 18.96 instead?} \DL{MCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$. The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCs?}

@@
